R Notebook

### 2021-03-10 eda.Rmd
Eda on state

- Filtered data such that `api_temp = oxymorphone`
- Dropped `country` and `api_temp`
- Removed observations with missing `ppm` (14)

@@

@@

>>>>

- Filtered data such that `api_temp = oxymorphone`
- Dropped `country` and `api_temp`
- Removed observations with missing `ppm` (14)
- Dropped unused levels

@@

# Drop unusued levels:
streetrx <- droplevels(streetrx)

@@

## City

First, check for standard missing values

```{r}
sum(is.na(streetrx$city))
```

Some issues:

- Missing city is the most common (1413 times)
- Nonstandard casing (sometimes lowercase)
- Numbers occasionally appear
- State occasionally included in city

Honestly this column is a bit of a mess, with many values appearing a very minimal number of times:

```{r}
table(streetrx$city, exclude = '') %>% hist()
```

Don't include for now

## State
